An agent-based model of military mechanization

### 2018-07-10 paper2/paper2.tex
multicollinearity

Military mechanization is the degree to which a state's army is comprised of
ground combat vehicles as opposed to infantry. Mechanization is both a 
theoretically important topic in international relations scholarship and a practical 
concern for policymakers. \citet{sechser2010army} influentially argue that
inter-state dynamics (e.g., rivalries) better explain mechanization choices than do
intra-state factors (e.g., culture). This paper demonstrates that
the multivariate statistical approach employed in \citet{sechser2010army} is inadequate. 
It presents an alternate agent-based model of military mechanization that has superior explanatory power.

@@

@@

@@

>>>>

Military mechanization is the degree to which a state's army is comprised of
ground combat vehicles as opposed to infantry. Mechanization is both a 
theoretically important topic in international relations scholarship and a practical 
concern for policymakers. \citet{sechser2010army} influentially argue that
inter-state dynamics (e.g., rivalries) better explain mechanization choices than do
intra-state factors (e.g., culture). This paper demonstrates that
the multivariate statistical approach employed in \citet{sechser2010army} is
	inadequate and that agent-based modeling is needed to capture
	international security competition as a complex system. Candidate
	agent-based models are presented.

@@

Two central claims of this paper are that the multivariate statistical approach
of \citet{sechser2010army} is inadequate and agent-based modeling is needed.
They are addressed in turn.

\citet{sechser2010army} gather observational panel data that consists of a measure 
of military mechanization $y$ indexed by state $i$ and observation time $k$, as well as
time-indexed covariates $x$. The association of covariates with mechanization is
estimated via ordinary least squares (OLS) linear regression:

\begin{equation}
	y_{ik} = \beta_0 + \beta_j x_{ijk} + \epsilon \hspace{1em}
\end{equation}

Multicollinearity - everything correlated with each other

The fitted model attempts to characterize the separate
effect of each factor upon mechanization. However, evidence suggests that
the covariates in fact are strongly cross-correlated. The problem of
multi-collinearity can be expressed both

@@

\subsection{Outline}

@@

Practical and academic consequences
